Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-01 awipev-CO2.Rmd
Save replaced by saveRDS

save(file= paste0(path, "fb_data/d_all.rds"), d_all)

@@

pdelta_at_snapo
pdelta_at_snapo_dygraph
p_at_ts
pdelta_ct_snapo
pdelta_ct_snapo_dygraph
p_ct_ts
#ggsave(paste0("figures/delta_at_awipev_snapo.png"), pdelta_at_snapo, units="cm")
#ggsave(paste0("figures/delta_ct_awipev_snapo.png"), pdelta_ct_snapo, units="cm")
```
```{r save all, echo=FALSE, message= FALSE, warning=FALSE}
# d_hour is the real data set that is read at the beginning of the script
# d_all comprises additional columns calculated in this script
# These additional variablrs are useful elsewhere (for example in "presentation")
# Hence, here we save it for this use
saveRDS(file= paste0(path, "fb_data/d_all.rds"), d_all)
```

@@

### Data processing
We use the AWI database [Quick overview AWI NRT database](https://dashboard.awi.de/?dashboard=9736)

* **crontab awipev@awipev-co2.obs-vlfr.fr**
Si on veut remplacer intégralement les fichiers de pCloud par ceux de awipev-co2 : ajouter “--delete” à la commande rsync.
Pattern des commandes : # m h dom mon dow command

@@

* La page web index.html est faite sur le serveur awipev/web grâce au script awipev-CO2_web.Rmd puis transférée et renommée dans awipev/awipev-CO2_web
* Création du répertoire web qui contient ce qu’il faut pour générer la page web:
    + AWIPEV-Logo.jpg
    + Discrete_sampling_AWIPEV.csurv
    + awipev-CO2_web.Rmd
    + awipev-co2.sh (lancer par bash awipev-co2.sh)
* Accessible https://awipev-co2.obs-vlfr.fr 
* On utilise un shell script awipev-co2.sh:
    #!/bin/bash 
    # script de lancement via crontab echo '---------deb awipev-co2.sh -----------' 
    # On lance la fabrication du html cd web; R -e 
    'library("rmarkdown");library("knitr");rmarkdown::render("awipev-CO2_web.Rmd")'; cp awipev-CO2_web.html ../awipev-CO2_web/index.html 
    echo '---------fin awipev-co2.sh -----------'

A la main dans le terminal, cela donne :
* ssh awipev@awipev-co2.obs-vlfr.fr
* R --vanilla < web/awipev-CO2_web.Rmd

>>>>

saveRDS(file= paste0(path, "fb_data/d_all.rds"), d_all)

@@

pdelta_at_snapo
pdelta_at_snapo_dygraph
p_at_ts
pdelta_ct_snapo
pdelta_ct_snapo_dygraph
p_ct_ts
#ggsave(paste0("figures/delta_at_awipev_snapo.png"), pdelta_at_snapo, units="cm")
#ggsave(paste0("figures/delta_ct_awipev_snapo.png"), pdelta_ct_snapo, units="cm")
```
```{r save all, echo=FALSE, message= FALSE, warning=FALSE}
# d_hour is the real data set that is read at the beginning of the script
# d_all comprises additional columns calculated in this script
saveRDS(file= paste0(path, "fb_data/d_all.rds"), d_all)
```

@@

### Data processing

#### Script ny-alesund_cc.R which runs on awipev@awipev-co2.obs-vlfr.fr
* reads data from the AWI NRT database [Quick overview AWI NRT database](https://dashboard.awi.de/?dashboard=9736) 
* calibrates pCO2 data
* data cleaning:
  + Argo Global Range Test.
  + filter salinities above 28
  + filter temperatures above 10
  + filter seaFET Volt (outliers)
  + filter seaFET pH (outliers)
  + filter durafet (outliers)
* Quality flags
    + 1: good data
    + 3: impossible date and time test
    + 4: data not usable according to manufacturer (flush mode, zero mode, calibration mode...) 
    + 6: failing the manufacturer range test (not used)
    + 7: failing the regional range test 
    + 12: failing the spike test (NAs from despike)
    + 13: failing the gradient test
    + 15: the instrument was not deployed or operated
    + 99: failing the final visual inspection of the data. 
* Despike using oce::despike with n=2, k=5761
* Files generated:
    + previous_NRT_data.rds: all NRT data without alteration from the beginning (2015)
    + all_nydata_minute.rds: all data after filtering and despike describe above (every minute)
    + all_nydata_hour.rds: hourly means of all data after filtering and despike describe above (every minute)
    + nydata_minute.rds: selected data after filtering and despike describe above (every minute). **Useful?**
    + nydata_hour.rds: selected hourly means of all data after filtering and despike describe above (every minute).  This is for further data processing.

#### Script awipev-co2.Rmd which runs locally
* sal_mix: when ferrybox data (sal_fb) are missing, they are replaced by data from the profiling ctd for depths > 8 m (sal_insitu_ctd_9m)
* temp_mix: when data of in situ temperature at 11 m (temp_insitu_11m) are missing, they are replaced by data from the profiling ctd for depths > 8 m
* calibrate seafet pH
* calibrate durafet pH

**crontab awipev@awipev-co2.obs-vlfr.fr**
Si on veut remplacer intégralement les fichiers de pCloud par ceux de awipev-co2 : ajouter “--delete” à la commande rsync.
Pattern des commandes : # m h dom mon dow command

@@

* La page web index.html est faite sur le serveur awipev/web grâce au script awipev-CO2_web.Rmd puis transférée et renommée dans awipev/awipev-CO2_web
* Création du répertoire web qui contient ce qu’il faut pour générer la page web:
    + AWIPEV-Logo.jpg
    + Discrete_sampling_AWIPEV.csurv
    + awipev-CO2_web.Rmd
    + awipev-co2.sh (lancer par bash awipev-co2.sh)
* Accessible https://awipev-co2.obs-vlfr.fr 
* On utilise un shell script awipev-co2.sh :

    #!/bin/bash

    # script de lancement via crontab echo '---------deb awipev-co2.sh -----------'

    # On lance la fabrication du html cd web; R -e 
    'library("rmarkdown");library("knitr");rmarkdown::render("awipev-CO2_web.Rmd")'; cp awipev-CO2_web.html ../awipev-CO2_web/index.html

    echo '---------fin awipev-co2.sh -----------'

A la main dans le terminal, cela donne :

* ssh awipev@awipev-co2.obs-vlfr.fr
* R --vanilla < web/awipev-CO2_web.Rmd
